### 2022-01-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@6166c2549c61ce3da71f45b9eebf407f2b9230d5 🚀

Following the definition of Dunne (2006), a metaweb is the ecological
network analogue to the species pool; specifically, it inventories
\emph{potential} interactions between species for a spatially delimited
area (and so captures the \(\gamma\) diversity of interactions). The
metaweb is not a prediction of the network at a specific point within
the spatial area it covers: it will have a different structure, notably
by having a larger connectance (see \emph{e.g.} Wood et al., 2015), from
any of these local networks. These local networks (capturing the
\(\alpha\) diversity of interactions) are a subset of the metaweb's
species and interactions, and have been called ``metaweb realizations''
(Poisot et al., 2015). Differences between local networks and their
metawebs are due to chance, species abundance and co-occurrence, local
environmental conditions, and local distribution of functional traits,
among others.

Because the metaweb represents the joint effect of functional,
phylogenetic, and macroecological processes (Morales-Castilla et al.,
2015), it holds valuable ecological information. Specifically, it is the
``upper bounds'' on what the composition of the local networks can be
(see \emph{e.g.} McLeod et al., 2021). These local networks may be
reconstructed given appropriate knowledge of local species composition,
providing information on structure of food webs at finer spatial scales.
This has been done for example for tree-galler-parasitoid systems
(Gravel et al., 2018), fish trophic interactions (Albouy et al., 2019),
tetrapod trophic interactions (O'Connor et al., 2020), and crop-pest
networks (Grünig et al., 2020). In this contribution, we highlight the
\emph{probabilistic} nature of metawebs, discuss how a family of machine
learning tools (graph embeddings and transfer learning) can be used to
overcome data limitations to metaweb inference, and highlight how the
use of metawebs introduces important questions for the field of network
ecology.

@@

@@

>>>>

Following the definition of Dunne (2006), a metaweb is the ecological
network analogue to the species pool; specifically, it inventories
\emph{potential} interactions between species for a spatially delimited
area (and so captures the \(\gamma\) diversity of interactions). The
metaweb is not a prediction of the network at a specific point within
the spatial area it covers: it will have a different structure, notably
by having a larger connectance (see \emph{e.g.} Wood et al., 2015) and
complexity (see \emph{e.g.} Galiana et al., 2022), from any of these
local networks. These local networks (capturing the \(\alpha\) diversity
of interactions) are a subset of the metaweb's species and interactions,
and have been called ``metaweb realizations'' (Poisot et al., 2015).
Differences between local networks and their metawebs are due to chance,
species abundance and co-occurrence, local environmental conditions, and
local distribution of functional traits, among others.

Because the metaweb represents the joint effect of functional,
phylogenetic, and macroecological processes (Morales-Castilla et al.,
2015), it holds valuable ecological information. Specifically, it is the
``upper bounds'' on what the composition of the local networks can be
(see \emph{e.g.} McLeod et al., 2021); this information can help
evaluate the ability of ecological assemblages to withstand the effects
of, for example, climate change (Fricke et al., 2022). These local
networks may be reconstructed given appropriate knowledge of local
species composition, providing information on structure of food webs at
finer spatial scales. This has been done for example for
tree-galler-parasitoid systems (Gravel et al., 2018), fish trophic
interactions (Albouy et al., 2019), tetrapod trophic interactions
(O'Connor et al., 2020), and crop-pest networks (Grünig et al., 2020).
In this contribution, we highlight the \emph{probabilistic} nature of
metawebs, discuss how a family of machine learning tools (graph
embeddings and transfer learning) can be used to overcome data
limitations to metaweb inference, and highlight how the use of metawebs
introduces important questions for the field of network ecology.

@@

\leavevmode\hypertarget{ref-Fricke2022EffDef}{}%
Fricke, E. C., Ordonez, A., Rogers, H. S., \& Svenning, J.-C. (2022).
The effects of defaunation on plants' capacity to track climate change.
\emph{Science}.
\url{https://www.science.org/doi/abs/10.1126/science.abk3510}

@@

\leavevmode\hypertarget{ref-Galiana2022EcoNet}{}%
Galiana, N., Lurgi, M., Bastazini, V. A. G., Bosch, J., Cagnolo, L.,
Cazelles, K., Claramunt-López, B., Emer, C., Fortin, M.-J., Grass, I.,
Hernández-Castellano, C., Jauker, F., Leroux, S. J., McCann, K., McLeod,
A. M., Montoya, D., Mulder, C., Osorio-Canadas, S., Reverté, S.,
\ldots{} Montoya, J. M. (2022). Ecological network complexity scales
with area. \emph{Nature Ecology \& Evolution}, 1--8.
\url{https://doi.org/10.1038/s41559-021-01644-4}
